\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification for the Yelp Dataset Challenge}

### 2015-12-24 paper/article_2.tex
final version
paper updates

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Userless Classificaton for the Yelp Dataset Challenge} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

@@

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classificaton for the Yelp Dataset Challenge}} % Article title

@@

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs samplingmethod (GS) and the Non Negative Matrix Factorisation (NMF). We then present two methods for classifying restaurants. We first resorted to a supervised approach with a one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts. The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant. If the different feature extraction methods performs differently for the supervised and unsupervised approach, we observe some very promising results. The results could be used as the first step to an automated categorization system on the Yelp website.

>>>>

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Userless Classification for the Yelp Dataset Challenge} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

@@

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classification for the Yelp Dataset Challenge}} % Article title

@@

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs samplingmethod (GS) and the Non Negative Matrix Factorisation (NMF). We then present two methods for classifying restaurants. We first resorted to a supervised approach with one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts. The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant. If the different feature extraction methods performs differently for the supervised and unsupervised approach, we observe some very promising results. The results could be used as the first step to an automated categorization system on the Yelp website.
